Stack Safety as a Security Property

### 2020-07-07 main.tex
Instantiate variant in example

@@

%\leo{TODO: We really need a better layout than centered paragraphs.}

@@

% Fixed by Andrew:
%\COQ{This is the same as the coq version minus a redundant case.}

@@

\definition{Trace Integrity}
\label{def:trace-integrity}
Let $\contour$ be a contour and $\MPT$ be a (potentially infinite)
$\MPOTRACE$. We will say $\MPT$ satisfies {\em trace integrity} with
respect to $\contour$ if its final state (if any) agrees with its
initial one on all components marked $\HIGHSEC$ in $\contour$:
%
\[
\mathit{int} ~ \contour ~ \MPT \triangleq
\left \{ \begin{array}{ll}
  \mathit{True}, & \text{if $\MPT$ is infinite}\\
  \forall \component. ~ \contour(\component) = \HIGHSEC \rightarrow m_0(\component) = m_f(\component), & \text{otherwise} \\
\end{array}
\right .
\]
\leo{TODO: DISCUSS: Figure out notation for first/last machine state in a trace}

@@

Trace integrity characterizes the trace corresponding to a single
callee. Going back to our running example, such a trace would be, for
instance, the entire trace of {\tt h} from instruction 40 to
instruction 47. This trace is repeated in \Cref{fig:intex}, and
recolored: \leo{Explain colors here - not sure I agree with the
  current choice}
\leo{Old relevant text:
For an example see \cref{fig:intex}, in which {\tt h} writes its return
value to {\tt g}'s return location the stack rather than its own. That address
is high integrity (red), and so writing to it causes the property to fail.
}

@@

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in red and low confidentiality in green. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but the rest might have
any value, in yellow. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in pink, and while 109
is consistent, 108 will not hold 43 in all variants, so the trace does not obey
trace confidentiality.

@@

>>>>

\paragraph*{Head and Last}

We take the first element of a trace with \(\head(\Trace)\), which is a total
function since traces are non-empty, and the final element (if one exists) with
\(\last(\Trace)\), which is partial.

@@

@@

@@

\definition{Trace Integrity}
\label{def:trace-integrity}
Let $\contour$ be a contour and $\MPT$ be a (potentially infinite)
$\MPOTRACE$. We will say $\MPT$ satisfies {\em trace integrity} with
respect to $\contour$ if its final state (if any) agrees with its
initial one on all components marked $\HIGHSEC$ in $\contour$:
%
\[\begin{split}
  \mathit{int} ~ \contour ~ \MPT \triangleq &
    \mpostate{\mach_e}{\pol_e}{\obs_e} = \head(\MPT) \Rightarrow \\
  & \mpostate{\mach_r}{\pol_r}{\obs_r} = \last(\MPT) \Rightarrow \\
  & \forall \component. ~ \contour(\component) = \HIGHSEC \rightarrow
    \mach_e(\component) = \mach_r(\component) \\
\end{split}\]
\leo{TODO: DISCUSS: Figure out notation for first/last machine state in a trace}
\sna{We could do it like this, with finiteness implicit in the existence of
     a final state.}

@@

Trace integrity characterizes the trace corresponding to a single
callee. Going back to our running example, such a trace would be, for
instance, the entire trace of {\tt h} from instruction 40 to
instruction 47. This trace is repeated in \Cref{fig:intex}, with the initial
and final states colored to show the contour; high confidentiality
components in magenta, low in teal. At the end of the trace addresses 103
and 108 have both changed; since 103 was high confidentiality, the trace
does not enjoy trace integrity.

@@

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in magenta and low confidentiality in teal. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but all other addresses
hold -5, in orange. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in gray, and while 109
is consistent, 108 holds either 43 or -4, so the trace does not obey
trace confidentiality.

\sna{I like instantiating the variant, tomorrow I will extend it to the
     lazy example as well.}

@@

    \sna{Use the \(n\)-transition language above in all of these.}
